Group assignment

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

```{r echo=FALSE}
kable(count(df2,acctype_f) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

### • Country
### The countries with the most records are Italy and Germany. Together they make up 66% of all records.
```{r}
kable(count(df2, country) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

### • Season and class
### As we observed earlier, the dataset did not include two months for summer and two months for autumn, consequently, spring and winter have the most observations.
```{r echo=FALSE}
kable(count(df2, season) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

### The most obsevations belong to 'comfort' class, which corresponds to 3 and 3.5 stars, and to 'first class', which corresponds to 4 and 4.5 stars. There are also 15889 missing values. They appeared, because the hotels with 0 stars were not used for the 'class' variable, as the mean price for them is higher than for places with 1, 1.5, 2, and 2.5 stars, which does not make sense. Therefore, these observations were omitted.
```{r echo=FALSE}
kable(count(df2, class)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

## *Findings*

@@

```{r}
datasummary(trueprice*country ~ Mean + Max + Min, data=df2)%>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

@@

```{r echo=FALSE}
datasummary(trueprice*season ~ Mean, data=df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```

>>>>

```{r echo=FALSE}
kable(count(df2,acctype_f) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

### • Country
### The countries with the most records are Italy and Germany. Together they make up 66% of all records.
```{r echo=FALSE}
kable(count(df2, country) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

### • Season and class
### As we observed earlier, the dataset did not include two months for summer and two months for autumn, consequently, spring and winter have the most observations.
```{r echo=FALSE}
kable(count(df2, season) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

### The most obsevations belong to 'comfort' class, which corresponds to 3 and 3.5 stars, and to 'first class', which corresponds to 4 and 4.5 stars. There are also 15889 missing values. They appeared, because the hotels with 0 stars were not used for the 'class' variable, as the mean price for them is higher than for places with 1, 1.5, 2, and 2.5 stars, which does not make sense. Therefore, these observations were omitted.
```{r echo=FALSE}
kable(count(df2, class)) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

## *Findings:*

@@

```{r echo=FALSE}
datasummary(trueprice*country ~ Mean + Max + Min, data=df2) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r echo=FALSE}
datasummary(trueprice*season ~ Mean, data=df2) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```
